An indexed construction of semi-cubical types

### 2021-07-06 paper/paper.tex
[paper] One more figure cleaned up

\usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
\usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, fancyhdr, lastpage, amssymb}
\usepackage{listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace}
\usepackage[compact]{titlesec}
\usepackage[margin=0.5in]{geometry}

@@

% Logical implication
\newcommand{\imp}{\ensuremath{\rightarrow}}

@@

% The eqntable environment, displaying the various
\NewDocumentEnvironment{eqntable}{m}{\table[h!]
\tabularx{\textwidth}{@{} l X c X @{}}\toprule}
{\endtabularx\hrule\caption{#1}\endtable}

@@

\begin{eqntable}{Definition of a truncated cubical set (boxes)}
  \mc{Full homogeneous $n$-boxes}
  \eqnline{\myfullbox{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
  \eqnline{\myfullbox{l}{n}}{D}{\defeq}{\mybox{l}{n,n}(D)}
  \\
  \mc{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}
  \eqnline{\mybox{l}{n,p,[p \leq n]}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
  \eqnline{\mybox{l}{n,0}}{D}{\defeq}{\unittype}
  \eqnline{\mybox{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}{n,p'}(D).\,\mylayer{l}{n,p'}(D)(d)}
  \\
  \eqnline{\mylayer{l}{n,p,[p < n]}}{\shortstack{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\shortstack{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\; \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}
  \\
  \eqnline{\mycube{l}{n,p,[p \leq n]}}{\shortstack{(D:\partialcubset{l}{n}) \\(E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}
  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E.\ensuremath{\mathsf{rel}}(d)}
  \eqnline{\mycube{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma b:\mylayer{l}{n,p}(D)(d).\,\mycube{l}{n,p+1}(D)(E)(d,b)}
\end{eqntable}

\begin{figure*}
  \centerline{ \framebox{$
        \begin{array}{llcl}
          \downbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}   & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\end{array} & :      & \mybox{l}{n-1,p}(\hd(D))                                                              \\
          \downbox{l,\epsilon,q}{n,0}                         & D~\unitpoint                    & \defeq & \unitpoint                                                                            \\
          \downbox{l,\epsilon,q}{n,p'+1}                      & D~(d,b)                         & \defeq & (\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q-1}{n,p'}(D)(d)(b))        \\
          \\
          \downlayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}{n,p}(D))\\(b:\mylayer{l}{n,p}(D)(d))\end{array} & :      & \mylayer{l}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))                       \\
          \downlayer{l,\epsilon,q}{n,p}                       & D~d~c                           & \defeq & \!\!\begin{array}{l}(\overrightarrow{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L)),\\\;\overrightarrow{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R)))\end{array}                                                         \\
          \\
          \downcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}{n,p}(D))\\(b:\mycube{l}{n,p}(D)(E)(d))\end{array} & :      & \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))                \\
          \downcube{l,\epsilon,q}{n,p,[p=q]}                  & D~E~d~(b,\_)                    & \defeq & b_{\epsilon}                                                                          \\
          \downcube{l,\epsilon,q}{n,p,[p<q]}                  & D~E~d~(b,c)                     & \defeq & (\downlayer{l,\epsilon,q}{n,p}(D)(d)(b),\downcube{l,\epsilon,q}{n,p+1}(D)(E)(d,b)(c)) \\
          \\
        \end{array}
      $}}
  \caption{Definition of a homogeneous bare cubical set ($q$-th projection)}
  \label{fig:barecubicalsetfaces}
\end{figure*}

>>>>

\usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
\usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, fancyhdr, lastpage, amssymb}
\usepackage{listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell}
\usepackage[compact]{titlesec}
\usepackage[margin=0.5in]{geometry}

@@

% Logical implication
\newcommand{\imp}{\ensuremath{\rightarrow}}
\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}

@@

% The eqntable environment, displaying the various
\NewDocumentEnvironment{eqntable}{m}{\table[h!]
\tabularx{\textwidth}{@{} l c c X @{}}\toprule}
{\endtabularx\hrule\caption{#1}\endtable}

@@

\begin{eqntable}{Definition of a truncated cubical set (boxes)}
  \mc{Full homogeneous $n$-boxes}
  \eqnline{\myfullbox{l}{n}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
  \eqnline{\myfullbox{l}{n}}{D}{\defeq}{\mybox{l}{n,n}(D)}
  \\
  \mc{Homogeneous partial $n$-boxes and homogeneous partial $n$-cubes}
  \eqnline{\mybox{l}{n,p,[p \leq n]}}{(D:\partialcubset{l}{n})}{:}{\sort{l}}
  \eqnline{\mybox{l}{n,0}}{D}{\defeq}{\unittype}
  \eqnline{\mybox{l}{n,p'+1}}{D}{\defeq}{\Sigma d:\mybox{l}{n,p'}(D).\,\mylayer{l}{n,p'}(D)(d)}
  \\
  \eqnline{\mylayer{l}{n,p,[p < n]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}

  \eqnline{\mylayer{l}{n,p}}{D~d}{\defeq}{\makecell{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d)) \\ \times\; \mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))}}

  \\

  \eqnline{\mycube{l}{n,p,[p \leq n]}}{\makecell{(D:\partialcubset{l}{n}) \\(E:\mycubsetcomp{l}{n}(D)) \\ (d:\mybox{l}{n,p}(D))}}{:}{\sort{l}}

  \eqnline{\mycube{l}{n,p,[p = n]}}{D~E~d}{\defeq}{E.\ensuremath{\mathsf{rel}}(d)}

  \eqnline{\mycube{l}{n,p,[p < n]}}{D~E~d}{\defeq}{\Sigma b:\mylayer{l}{n,p}(D)(d).\,\mycube{l}{n,p+1}(D)(E)(d,b)}
\end{eqntable}

\begin{eqntable}{Definition of a homogeneous bare cubical set ($q$-th projection)}
  \eqnline{\downbox{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D))}}{:}{\mybox{l}{n-1,p}(\hd(D))}

  \eqnline{\downbox{l,\epsilon,q}{n,p'+1}}{D~(d,b)}{\defeq}{(\downbox{l,\epsilon,q}{n,p'}(D)(d),\downlayer{l,\epsilon,q-1}{n,p'}(D)(d)(b))}

  \\

  \eqnline{\downlayer{l,\epsilon,q}{n,p,[p \leq q \leq n - 2]}}{\makecell{(D:\partialcubset{l}{n}) \\ (d:\mybox{l}{n,p}(D)) \\ (b:\mylayer{l}{n,p}(D)(d))}}{:}{\mylayer{l}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}

  \eqnline{\downlayer{l,\epsilon,q}{n,p}}{D~d~c}{\defeq}{\makecell{(\overright{\cohbox{l,\epsilon,L,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))($c_L$)), \\ \;\overright{\cohbox{l,\epsilon,R,q,p}{n,p}(D)(d)}(\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))($c_R$)))}}

  \\

  \eqnline{\downcube{l,\epsilon,q}{n,p,[p \leq q \leq n - 1]}}{\makecell{(D:\partialcubset{l}{n}) \\ (E:\mycubsetcomp{l}{n}(D)) \\(d:\mybox{l}{n,p}(D)) \\ (b:\mycube{l}{n,p}(D)(E)(d))}}{:}{\mycube{l}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))}

  \eqnline{\downcube{l,\epsilon,q}{n,p,[p=q]}}{D~E~d~(b,\_)}{\defeq}{$b_\epsilon$}

  \eqnline{\downcube{l,\epsilon,q}{n,p,[p<q]}}{D~E~d~(b,c)}{\defeq}{(\downlayer{l,\epsilon,q}{n,p}(D)(d)(b),\downcube{l,\epsilon,q}{n,p+1}(D)(E)(d,b)(c))}
\end{eqntable}
